Ms 1

### 2017-08-18 ms1/ms1_display.Rmd
overall by populations

```{r claims_by_age}
read_tsv('tables/claims_by_age.tsv') %>%
  mutate(age_group=case_when(between(.$age, 65, 75) ~ '65-75',
                             between(.$age, 76, 85) ~ '76-85',
                             between(.$age, 86, 95) ~ '86-95')) %>%
  group_by(year, age_group) %>%
  summarize_at(vars(n_bene, n_claims), sum) %>%
  ungroup() %>%
  mutate(cpkp=round(1000*n_claims/n_bene)) %>%
  select(year, age_group, cpkp) %>%
  spread(year, cpkp) %>%
  kable
```

## Consumption by sex

```{r claims_by_sex}
read_tsv('tables/claims_by_sex.tsv') %>%
  select(sex, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-sex), round) %>%
  kable
```

## Consumption by region

```{r claims_by_region}
read_tsv('tables/claims_by_region.tsv') %>%
  select(region, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-region), round) %>%
  kable
```

## Consumption by race

```{r claims_by_race}
read_tsv('tables/claims_by_race.tsv') %>%
  select(race, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-race), round) %>%
  kable
```

# Adjusted consumption changes

@@

>>>>

```{r claims_by_age}
change_demog = read_tsv('tables/model_overall_demography.tsv') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  model_ci() %>%
  filter(term=='year0') %>%
  select(name, adj_change=change_str)

claims_by = function(x) {
  read_tsv(str_interp("tables/claims_by_${x}.tsv")) %>%
    rename_(.dots=list(name=x)) %>%
    select(name, year, cpkp) %>%
    filter(year %in% c(2011, 2014)) %>%
    spread(year, cpkp) %>%
    mutate(pct_change=round((`2014`-`2011`)/`2011`*100, 2)) %>%
    mutate_at(vars(`2011`, `2014`), round) %>%
    mutate(group=x)
}

# do claims by age group separate
# this could be baked into the analysis step
claims_by_age = read_tsv('tables/claims_by_age.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  mutate(name=case_when(between(.$age, 65, 75) ~ 'age65_75',
                        between(.$age, 76, 85) ~ 'age76_85',
                        between(.$age, 86, 95) ~ 'age86_95')) %>%
  group_by(year, name) %>%
  summarize_at(vars(n_bene, n_claims), sum) %>%
  ungroup() %>%
  mutate(cpkp=1000*n_claims/n_bene) %>%
  select(year, name, cpkp) %>%
  spread(year, cpkp) %>%
  mutate(pct_change=round((`2014`-`2011`)/`2011`*100, 2)) %>%
  mutate_at(vars(`2011`, `2014`), round) %>%
  mutate(group='age')

# use a common interface for all the others
bind_rows(claims_by_age,
          claims_by('sex'),
          claims_by('race'),
          claims_by('region')) %>%
  left_join(change_demog, by='name') %>%
  select(group, name, `2011`, `2014`, pct_change, adj_change) %>%
  kable
```

# Adjusted consumption changes by drug

@@

## By drug
